Lightweight Scheduling for the PRAGMA Cloud Testbed

### 2015-09-24 paper.tex
Few mods to respond to reviewer comments

Booked~\cite{booked} from Twinkle Toes software seemed the best suited to our needs compare to all the calendar reservation systems we evaluated.  It was easy to setup, had  a good look and feel, and was customizable.  It also had some nice additional features like usage reporting, a REST API interface, LDAP and Active Directory support, fine grained roles and permissions management, and user and group quotas.  After working with Booked during our pilot setup, we did find some weaknesses.  First, the documentation was very sparse and any needed PHP changes were time consuming due to its heavily object-oriented structure (i.e., we had to go through many source code files to find the right place to change  or add functionality).

@@

Figure~\ref{Fig:Flow} shows the above steps in a use case sequence diagram where \textit{PRAGMA Booking} refers to our customized Booked instance.  PCC will monitor the health of the virtual cluster and when the reservation is close to expiring, will notify the user via email. The user then has an option to extend the reservation.  Otherwise, when the time expires or the user chooses to end its reservation, the virtual cluster will be shut down.

>>>>

Booked~\cite{booked} from Twinkle Toes software seemed the best suited to our needs compare to all the calendar reservation systems we evaluated.  It was easy to setup, had  a good look and feel, and was customizable.  It also had some nice additional features like usage reporting, a REST API interface, LDAP and Active Directory support, fine grained roles and permissions management, and user and group quotas.  After working with Booked during our pilot setup, we did find some weaknesses.  First, the documentation was very sparse and any needed PHP changes were time consuming due to its heavily object-oriented structure (i.e., we had to go through many source code files to find the right place to change  or add functionality).   The granularity of Booked reservations is currently limited to an hourly basis and for today's PRAGMA needs this is sufficient because the time it takes to start up the virtual cluster 
is tens of minutes and  the user reservation is expected to  be on the order of days. The reservation granularity can be optimized in the future in order to avoid a potential of underutilized resources when the virtual cluster startup becomes minutes.

@@

Figure~\ref{Fig:Flow} shows the above steps in a use case sequence diagram where \textit{PRAGMA Booking} refers to our customized Booked instance.  PCC will monitor the health of the virtual cluster and when the reservation is close to expiring, will notify the user via email. The user then has an option to extend the reservation if resources are available.  Otherwise, when the time expires or the user chooses to end the reservation, the virtual cluster will be shut down.
